Response to the defense feedback

### 2021-06-16 Chapter-3/Chapter-3.tex
Updates from Overleaf

If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the inputs. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then an attacker can infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affect the program counter (the rip register), which is the root cause of the side-channel leakages.

@@

\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
...
\end{lstlisting}

@@

  \centering\small\footnotesize

@@

The comparison result with CacheD~\cite{203878,217537} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. In the circumstance, we consider it takes only one leakage.
We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours when processing
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While these optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages occurs when the input messages equal to some certain values. It is possible that CacheD misses some
leakages as we have discussion the previous sections.
We notice that the number of instructions in these traces are different due to the different analysis starting functions and build options during the evaluation.
Table~\ref{eval:cacheD} shows that
\detect{} is faster than CacheD. \detect{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\detect{} on AES from OpenSSL
0.9.7, \detect{} is over 100x faster than CacheD.
\begin{table*}[ht]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}
    \resizebox{.9\columnwidth}{!}{%
    \begin{tabular}{@{}l|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
      \hline
      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
      Benchmark                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
      AES OpenSSL 0.9.7         & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
      AES OpenSSL 1.0.2f       & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
      RSA OpenSSL 0.9.7       & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
      RSA OpenSSL 1.0.2f     & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
      RSA Libgcrypt 1.6.1     & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
      RSA Libgcrypt 1.7.3         & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
    \end{tabular}
}
\end{table*}

>>>>

If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the inputs. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then an attacker can infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affect the program counter (the \textsf{rip} register), which is the root cause of the side-channel leakages.

@@

\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none,numbers=none][h]
...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
...
\end{lstlisting}

@@

  \centering\small

@@

The comparison result with CacheD~\cite{203878,217537} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. In the circumstance, we consider it takes only one leakage.
We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours when processing
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While these optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages occurs when the input messages equal to some certain values. It is possible that CacheD misses some
leakages as we have discussion the previous sections.
We notice that the number of instructions in these traces are different due to the different analysis starting functions and build options during the evaluation.
Table~\ref{eval:cacheD} shows that
\detect{} is faster than CacheD. \detect{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\detect{} on AES from OpenSSL
0.9.7, \detect{} is over 100x faster than CacheD.
\begin{table*}[ht]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}
    \resizebox{.9\columnwidth}{!}{%
    %TODO
    \begin{tabular}{l|rrr|rrr}
      \hline
      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
      Benchmark                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
      AES OpenSSL 0.9.7         & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
      AES OpenSSL 1.0.2f       & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
      RSA OpenSSL 0.9.7       & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
      RSA OpenSSL 1.0.2f     & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
      RSA Libgcrypt 1.6.1     & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
      RSA Libgcrypt 1.7.3         & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \qquad \qquad \qquad \tool: 12,489}                                 \\ \hline
    \end{tabular}
}
\end{table*}
